Validating FF-Replan vs.\@ a State-Of-The-Art Probabilistic Planner in Translated Real World Domains

### 2014-03-30 FinalPaper/paper.tex
abstract changed

\begin{abstract}
	This paper argues that for many real life domains dead-ends are the end of
	the world, and by for example human interaction the goal can still be
	reached. By relaxing the definition of a dead-end, we argue that for many
	real life domains a simpler planning algorithm, like FF-Replan, can be
	sufficient, and that it's not needed to have newer and sophisticated
	probabilistic planners.
\end{abstract}

>>>>

\begin{abstract}
	In contrast to current demand for probabilistically interesting domains in the International Probabilistic Planning Competitions, this papier argues for using real-world appropriate domains. By relaxing the definition of a dead-end, we argue that for many
real life domains a simpler planning algorithm can be sufficient and even better than sophisticated probabilistic planners.

In this paper we evaluate the strength of FF-Replan, winner of IPPC-04 and unenrolled winner of IPPC-06, a replanner that uses the classical planner FF on a determinized probabistic problem against a state of the art probabilistic planner GOURMAND, the successor of the Labelled Real-Time Dynamic Probabilistic planner Glutton, runner up of the IPPC-11. By translating the Navigation and Traffic domain from IPPC-11 to a matching real-world equavalent and evaluating these using the proposed probabilistically interesting baseline test as proposed by Little et. all we will evaluate whether FF-Replan is in fact capable enough to solve enough of these so called classical planning problems in disguise.
\end{abstract}
